# Code-a-thon Project Template

This project is intended to help you apply your skills in R in a way that would be conducive for collaborating or creating reproducible analyses.


## Data Used

Identify a dataset to analyze. Remember that if you share the data you must **not violate any privacy restrictions**

If you don't have your own data, options for places to find data are listed on https://daseh.org.

You might start by setting up an R Project, importing your data, previewing the data, etc. 

```{r}
library(tidyverse)
view(biopsy)

```

**describe** what your data looks like and **where** you got it. Identify what the variables and samples are, or point to a data dictionary. Describe how the data was originally created. 

```{r}
head(biopsy)

dim(biopsy)

#left off here day 1 and still figuring out data cleaning and or finalizing question of correlation between clump thickness or cell size and malignancy
```


# Data Cleaning/Wrangling

Perform any data subsetting, cleaning, or manipulation methods that were described in this course on your data. Examples are: renaming the columns, recoding values, reshaping the data, filtering the data etc. 

You might also research other methods to include here, especially if your data is very unique.

```{r}
names(biopsy) <- c("ID", "Clump_Thickness", "Cell_Size", "Cell_Shape",
                    "Marginal_Adhesion", "Single_Epi_Cell_Size",
                    "Bare_Nuclei", "Bland_Chromatin",
                    "Normal_Nucleoli", "Mitoses", "Class")

library(dplyr)

biopsy |>
  group_by(Class) |>
  summarize(
    mean_clump = mean(Clump_Thickness),
    mean_cell_size = mean(Cell_Size),
    n = n()
  )

cor(select(biopsy, where(is.numeric)))
```


# Data Visualization

Create some visualizations of your data using the esquisse app or the ggplot2 package.

```{r}
#figure out regression or overall visualization of data to reflect correlation

library(ggplot2)

ggplot(biopsy, aes(x = Class,
                   y = Clump_Thickness,
                   fill = Class)) +
  geom_boxplot() +
  labs(
    title = "Clump Thickness by Diagnosis",
    x = "Diagnosis",
    y = "Clump Thickness"
  )

ggplot(biopsy, aes(x = Class,
                   y = Cell_Size,
                   fill = Class)) +
  geom_boxplot() +
  labs(
    title = "Cell Size by Diagnosis",
    x = "Diagnosis",
    y = "Cell Size"
  )
```


# Data Analysis

Perform a **simple analysis** of your data. This can involve summarizing the data to describe aspects about it (quartiles, means, range etc.) or a simple statistical test. 

Don't forget to describe what analysis you performed and why. Provide some simple **interpretation** about what your analysis might indicate about your data.

```{r}

```


# Please include additional sections as desired.

```{r}

```


# Versions

Include some information about the version of R and the packages you are using by running sessionInfo().

```{r}
sessionInfo()
```

Render your document to an html or pdf using the "Knit" button.
